# Strings, Numbers, and collections

Funny things can happen when you construct strings. 
* The quotes are a signal to the interpreter, not part of the string itself
* To put in quotes, escape them. 
* Things like '\n' indicate "control characters." 
```{r}
myFavoriteName<- "Bashir Assad"
```



The President of the Russian Republic is 
```{r}
myFavoriteName
```

```{r}
cat("The fog came in\non little cats feet.")
```

```
```{r}
plot(1:50)
```
 1:5
[1] 1 2 3 4 5
> c("hello", "Charlie")
[1] "hello"   "Charlie"
> c("hello", 17)
[1] "hello" "17"   
> c("hello", "17"")
+ c("hello", "17")
Error: unexpected string constant in:
"c("hello", "17"")
c(""
> c("hello", "17")
[1] "hello" "17"   
> c("hello", "17")
[1] "hello" "17"   
> paste("hello", 120)
[1] "hello 120"
> paste("hello", 1:20)
 [1] "hello 1"  "hello 2"  "hello 3"  "hello 4"  "hello 5"  "hello 6"  "hello 7"  "hello 8" 
 [9] "hello 9"  "hello 10" "hello 11" "hello 12" "hello 13" "hello 14" "hello 15" "hello 16"
[17] "hello 17" "hello 18" "hello 19" "hello 20"
> paste("hello", 1:20, sep"-")
Error: unexpected string constant in "paste("hello", 1:20, sep"-""
> paste("hello", 1:20, sep'-')
Error: unexpected string constant in "paste("hello", 1:20, sep'-'"
> paste("hello", 1:20, sep="-")
 [1] "hello-1"  "hello-2"  "hello-3"  "hello-4"  "hello-5"  "hello-6"  "hello-7"  "hello-8" 
 [9] "hello-9"  "hello-10" "hello-11" "hello-12" "hello-13" "hello-14" "hello-15" "hello-16"
[17] "hello-17" "hello-18" "hello-19" "hello-20"
> paste("hello", 1:20, collapse="*")
[1] "hello 1*hello 2*hello 3*hello 4*hello 5*hello 6*hello 7*hello 8*hello 9*hello 10*hello 11*hello 12*hello 13*hello 14*hello 15*hello 16*hello 17*hello 18*hello 19*hello 20"
> list("hello", 1)
[[1]]
[1] "hello"

[[2]]
[1] 1

> KidsFeet
       name birthmonth birthyear length width sex biggerfoot domhand
1     David          5        88   24.4   8.4   B          L       R
2      Lars         10        87   25.4   8.8   B          L       L
3      Zach         12        87   24.5   9.7   B          R       R
4      Josh          1        88   25.2   9.8   B          L       R
5      Lang          2        88   25.1   8.9   B          L       R
6    Scotty          3        88   25.7   9.7   B          R       R
7    Edward          2        88   26.1   9.6   B          L       R
8   Caitlin          6        88   23.0   8.8   G          L       R
9   Eleanor          5        88   23.6   9.3   G          R       R
10    Damon          9        88   22.9   8.8   B          R       L
11     Mark          9        87   27.5   9.8   B          R       R
12      Ray          3        88   24.8   8.9   B          L       R
13      Cal          8        87   26.1   9.1   B          L       R
14      Cam          3        88   27.0   9.8   B          L       R
15    Julie         11        87   26.0   9.3   G          L       R
16     Kate          4        88   23.7   7.9   G          R       R
17 Caroline         12        87   24.0   8.7   G          R       L
18   Maggie          3        88   24.7   8.8   G          R       R
19      Lee          6        88   26.7   9.0   G          L       L
20  Heather          3        88   25.5   9.5   G          R       R
21     Andy          6        88   24.0   9.2   B          R       R
22     Josh          7        88   24.4   8.6   B          L       R
23    Laura          9        88   24.0   8.3   G          R       L
24    Erica          9        88   24.5   9.0   G          L       R
25    Peggy         10        88   24.2   8.1   G          L       R
26     Glen          7        88   27.1   9.4   B          L       R
27     Abby          2        88   26.1   9.5   G          L       R
28    David         12        87   25.5   9.5   B          R       R
29     Mike         11        88   24.2   8.9   B          L       R
30   Dwayne          8        88   23.9   9.3   B          R       L
31 Danielle          6        88   24.0   9.3   G          L       R
32  Caitlin          7        88   22.5   8.6   G          R       R
33    Leigh          3        88   24.5   8.6   G          L       R
34    Dylan          4        88   23.6   9.0   B          R       L
35    Peter          4        88   24.7   8.6   B          R       L
36   Hannah          3        88   22.9   8.5   G          L       R
37 Teshanna          3        88   26.0   9.0   G          L       R
38   Hayley          1        88   21.6   7.9   G          R       R
39   Alisha          9        88   24.6   8.8   G          L       R
> myExample <- data.fame( a=1:5, letters=c("a" "b" "c" "d" "e"))
Error: unexpected string constant in "myExample <- data.fame( a=1:5, letters=c("a" "b""
> myExample <- data.frame( a=1:5, letters=c("a" "b" "c" "d" "e"))
Error: unexpected string constant in "myExample <- data.frame( a=1:5, letters=c("a" "b""
> myExample <- data.frame( a=1:5, letters=c("a", "b", "c", "d", "e"))
> myExample
  a letters
1 1       a
2 2       b
3 3       c
4 4       d
5 5       e
> list(theData=myExample, today=10)
$theData
  a letters
1 1       a
2 2       b
3 3       c
4 4       d
5 5       e

$today
[1] 10

> "I want to go to the zoo."
[1] "I want to go to the zoo."
> "I want to go to the zoo.'
+ Mommy""
+ Mommy"
Error: unexpected string constant in:
"Mommy""
Mommy""
> "I want to go to the zoo.'
+ Mommy"
[1] "I want to go to the zoo.'\nMommy"
> complicated <- "The fog comes in\non little cats feet"
> complicated
[1] "The fog comes in\non little cats feet"
> cat(complicated)
The fog comes in
on little cats feet
> ""
[1] ""
> "\"I do not want to go to the doctor\", said Billy to Mommmy"
[1] "\"I do not want to go to the doctor\", said Billy to Mommmy"
> cat("\"I do not want to go to the doctor\", said Billy to Mommmy")
"I do not want to go to the doctor", said Billy to Mommmy
> source('~/R-03.R')
Error in source("~/R-03.R") : ~/R-03.R:3:7: unexpected symbol
2: 
3: Funny things
        ^
> source('~/R-03.R')
Error in source("~/R-03.R") : ~/R-03.R:3:7: unexpected symbol
2: 
3: Funny things
        ^
> source('~/R-03.R')
Error in source("~/R-03.R") : ~/R-03.R:3:7: unexpected symbol
2: 
3: Funny things
        ^
> source('~/R-03.R', echo=TRUE)
Error in source("~/R-03.R", echo = TRUE) : 
  ~/R-03.R:3:7: unexpected symbol
2: 
3: Funny things
        ^
> source('~/R-03.R')
Error in source("~/R-03.R") : ~/R-03.R:3:7: unexpected symbol
2: 
3: Funny things
        ^
> myFavoriteName= "Vladimir Putin"
> myFavoriteName
[1] "Vladimir Putin"